Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages

### 2021-06-11 paper/appendix.Rmd
Got sp_models sensibility analysis

```{r}
loadd(
  resume_bm_rich_mod_mono_trends,
  model_bm_rich_no_covar_no_inc_mono_trends,
  reg_table_bm_rich_mono_trends,
  reg_table_bm_rich_mono_stable_trends,
  reg_table_bm_rich_trends,
  reg_table_bm_rich,
  anova_table_bm_rich_mono_trends,
  anova_table_bm_rich_mono_stable_trends,
  anova_table_bm_rich_trends,
  anova_table_bm_rich,
  anova_bm_rich_mod,
  st_trends_rich_bm,
  st_mono_trends_rich_bm,
  st_mono_trends_stable_rich_bm
)

loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends, pred_bm_rich_mono_stable_trends)
```

>>>>

```{r}
loadd(
  resume_bm_rich_mod_mono_trends,
  model_bm_rich_no_covar_no_inc_mono_trends,
  reg_table_bm_rich_mono_trends,
  reg_table_bm_rich_mono_stable_trends,
  reg_table_bm_rich_trends,
  reg_table_bm_rich,
  anova_table_bm_rich_mono_trends,
  anova_table_bm_rich_mono_stable_trends,
  anova_table_bm_rich_trends,
  anova_table_bm_rich,
  anova_bm_rich_mod
)
loadd(st_trends_rich_bm, st_mono_trends_rich_bm,
  st_mono_trends_stable_rich_bm)

loadd(pred_bm_rich_mono_trends, pred_bm_rich, pred_bm_rich_trends,
  pred_bm_rich_mono_stable_trends)

### 2021-06-11 paper/manuscript.Rmd
Got sp_models sensibility analysis

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)

```

@@

sp_bm <- sp_relation_plot2 %>%
  filter(x == "log_bm_std")
p_sp_bm <- sp_bm$gg
names(p_sp_bm) <- sp_bm$y
```

@@

sp_rich <- sp_relation_plot2 %>%
  filter(x == "log_rich_std")
p_sp_rich <- sp_rich$gg
names(p_sp_rich) <- sp_rich$y
```

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)
```

@@

sp_bm <- sp_relation_plot2 %>%
  filter(response == "log_bm_std")
p_sp_bm <- sp_bm$gg
names(p_sp_bm) <- sp_bm$y
```

@@

sp_rich <- sp_relation_plot2 %>%
  filter(term == "log_rich_std")
p_sp_rich <- sp_rich$pred_plot
names(p_sp_rich) <- sp_rich$y
```
